Understanding the impact of electronically-delivered parenting advice

### 2019-01-17 paper/cogsci2019/cogsci2019.Rmd
first draft of intro

keywords: >
    digital parenting advice; joint action; lexical diversity; guided play;

@@

- children learn through play -- physics, object features

## Guided Play Scaffolds Learning
- guided play activities can scaffold children's language and reasoning

## Improving Parenting Practices and Language Use
- early interventions on parenting practices can help children's outcomes

## Effectiveness of Digital Delivery
apps are an easy way to deliver curated, age-appropriate parenting advice — but can we measure an influence on parent's language? and do the interventions lead to children paying more attention?

>>>>

keywords: >
    digital parenting advice; joint attention; lexical diversity; guided play;

@@

- children learn through play -- physics, object features
Children want and need to play a lot: 
by interacting with other people or physcial objects, they explore, experiment and build up their understandings of how the world functions. 
Researches have suggested that play is important to learning,
"allowing children to imitate adult behaviors, practice motor skills, process emotional events, and learn much about their world."(Hirsh,2008)
## Guided Play Scaffolds Learning
- guided play activities can scaffold children's language and reasoning
What we cannot ignore, however,
is that children's efforts to explore the world are often "assisted and fostered by others who are more skillful than they are"(Kaye, 1970). 
With the help of an adult or "expert", children are able to engage with more advanced play and explore the functions of objects more.
These tutorial interactions have been shown to be a "a crucial feature of infancy and childhood"(Wood, 1970).
Thus, with the knowledge of both play and tutorial interactions, guided play, "where children actively engage in pleasurable and seemingly spontaneous activities under the direction of adults"(Hirsh,2008), 
have drawn researchers' interest. 
Weisberg showed that, with preschoolders, guided play scaffolds the environment while still allowing children to maintain a large degree of control, 
and it outperforms direct-instruction approaches in encouraging a variety of positive academic outcomes (Weisberg,Hirsh&Golinkoff, 2013).
Massey specifically showed that guided play could facilitate children's vocabulary and comprehensive language development and subsequent literacy skills (Massey, 2013).

## Improving Parenting Practices and Language Use
- early interventions on parenting practices can help children's outcomes
Thus, including guided play in parenting practices early on is important and should help with children's later performances. Suskind did a parent-directed home-visiting intervention experiment in 2015, 
and found that parents in experimental group have greater knowledge of language development and this effect sustained after the experiment is done. 
However, more interactive outcomes, like parent word type and token numbers, child word types, conversational turn counts and child vocalization counts, 
increased during the home-visiting but did not sustain after four months of intervention [there are more detailed sustainibility differences of these measure. should I make it more clear?] (Suskind, 2015).
The fact that changes did not sustain could be due to the intervention itself, 
or could merely be that home-visiting is not sustainable enough for parents to easily and constantly get parenting advice.

## Effectiveness of Digital Delivery
-apps are an easy way to deliver curated, age-appropriate parenting advice — but can we measure an influence on parent's language? and do the interventions lead to children paying more attention?

Digitally-delivered methods could address some logistic barriers to face-to-face delivery methods. 
Bretenstein reviewed 11 studies on them and showed good promise for the efficacy of interventions using digitally-delivered methods. 
However, the parent and child outcomes assessed in the review (e.g.infant positive behaviors, satisfaction, emotional symptoms etc.) did not address the nature or quality of parent-infant interactions at a detailed level,
like if the interventions lead to children paying more attention, or vocabulary changes in parents' language usages. 
Thus, we want to conduct this experiment to explore if and how digital scaffolding of activities affect the social and linguistic characteristics of parent-child ineractions.
